\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Work Experience}

\cve{Aug 2021 -- Present}{Software Developer}{INFORM GmbH - Optimization Software}{Aachen, Germany}
\cvitem{}{
    Redevelopment of a product that manages and optimizes the processes on container terminals.
    For this purpose, a distributed system is used, which by means of Kubernetes enables the independent scaling of individual services.
    The backend services are based on hexagonal architecture (comparable to Clean Architecture or Onion
    Architecture) and developed on the basis of Spring Boot and Kotlin.
    The micro frontends, written in Angular, communicate with their backend via GraphQL and display live data.
}
\cvspace

\cve{Jan 2019 -- Aug 2021}{Software Developer}{Panasonic Europe Ltd.}{Hamburg, Germany}
\cvitem{}{
    I worked on a dockerized, Kotlin-based, Spring Boot web application with an Angular frontend,
    controlling approval processes via Camunda BPMN with dynamic rules based on DMNs. We migrated
    the application into the AWS cloud and used Terraform to define its infrastructure as code.
}
\cvitem{\iconTestimonial}{\link{https://mcarle.io/testimonials/panasonic.pdf} (German)}
\cvspace

\cve{Apr 2017 -- Dec 2018}{Project Manager}{Enghouse Networks (Germany) GmbH \footnotesize (formerly XConnect GmbH)}{Düren, Germany}
\cvitem{}{
    I managed a project with several large telecommunications service providers and implemented their requirements based on JIRA.
    Internally, I was responsible for planning and developing a successor product for automated information procedures in accordance with §112 TKG
    and used technologies like CQRS, Apache Camel, Event Sourcing, Vaadin, and OSGi.
}
\cvitem{\iconTestimonial}{\link{https://mcarle.io/testimonials/enghouse.pdf} (German)}
\cvspace

\cve{Jan 2012 -- Mar 2017}{Software Developer}{XConnect GmbH \footnotesize (formerly sms eSolutions GmbH)}{Düren, Germany}
\cvitem{\footnotesize \emph{20h/week}}{
    I was responsible for various Java EE web applications targeting the telecommunication market in Germany.
    In collaboration with my colleagues, I planned, documented, and implemented new applications, as well as maintained and extended existing ones.
    Furthermore, I also acted as 2nd level support for our customers via mail and phone.
}
\cvitem{\iconTestimonial}{\link{https://mcarle.io/testimonials/sms-to-xconnect.pdf} (interim, German)}
\cvspace
\newpage

\subsection{Start-up}
\cve{Mar 2014 -- Jun 2016}{Co-Founder and CTO}{Bontoo Mobile Development UG (with limited liability)}{Würselen, Germany}
\cvitem{}{
    The start-up focused on developing mobile apps in the B2B market. My area of responsibility was IT project
    management and the development of backend systems and REST interfaces that were accessed by the mobile apps.
    I also advised potential customers on how a mobile application could facilitate daily work in their business area.
}

\subsection{Apprenticeship}
\cve{Jul 2009 -- Jan 2012}{Mathematical-Technical Software Developer (MATSE)}{sms eSolutions GmbH}{Düren, Germany}
\cvitem{}{
    I started my career with a dual study program, i.e. with an apprenticeship as Mathematical-Technical Software Developer
    (abbreviated as MATSE in German) and a parallel bachelor study in Scientific Programming.
}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}

\cve{2012 -- 2017}{Master of Science}{RWTH Aachen University}{Aachen, Germany}
\cvitem{}{Course of studies: \emph{Computer Science}}
\cvitem{\iconGraduation}{Master thesis: \emph{Improving Vehicle Diagnostics in Service Stations with Wearable Devices}}
\cvitem{\iconBuilding}{Tendering company: \emph{DSA Daten- und Systemtechnik GmbH, Germany}}
\cvspace

\cve{2009 -- 2012}{Bachelor of Science}{University of Applied Sciences Aachen}{Jülich, Germany}
\cvitem{}{Course of studies: \emph{Scientific Programming} \footnotesize (dual studies)}
\cvitem{\iconGraduation}{Bachelor thesis: \emph{Development and Optimization of a Software for High-Performance Storage and Processing of Mass Data for an Open System Landscape}}
\cvitem{\iconBuilding}{Tendering company: \emph{Enghouse Networks (Germany) GmbH, Germany}}
\cvspace

\cve{2001 -- 2009}{Abitur}{Archigymnasium Soest}{Soest, Germany}
\cvitem{}{Special subjects: \emph{Computer Science and Mathematics}}

%----------------------------------------------------------------------------------------
%	CERTIFICATES SECTION
%----------------------------------------------------------------------------------------
\section{Certificates}

\cvitem{2021}{\textbf{AWS Certified Solutions Architect - Associate}, \emph{AWS Certification}}
\cvitem{\iconCertificate}{\link{https://mcarle.io/certs/aws-solutions-architect-certificate.pdf}}

\cvspace

\cvitem{2012}{\textbf{In-Memory Data Management}, \emph{openHPI, Prof. Dr. h.c. mult. Hasso Plattner}}
\cvitem{\iconCertificate}{\link{https://mcarle.io/certs/in-memory-data-management-certificate.pdf}}


%----------------------------------------------------------------------------------------
%	SOFT SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Soft Skills}
\cvitemize{Proactive}{Very flexible}{High commitment}
\cvitemize{Curious by nature}{High team spirit}{Good conflict management}
\cvitemize{Communicative}{}{}


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitem{German}{Native}
\cvitem{English}{Advanced}


%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Technical Skills}

% Used fibonacci numbers: 1,2,3,5,8,13
\cvdoubleitem{}{\strut\subsectionstyle{Languages}}{}{\strut\subsectionstyle{Platforms}}
\cvdoubleitem{> 13 years}{Java, JavaScript, HTML, Bash, SQL}{> 13 years\cbstart}{Linux, Windows}
\cvdoubleitem{> 3 years}{Kotlin, TypeScript}{> 2 years\cbend}{AWS, Android}
\cvspace

\cvdoubleitem{}{\strut\subsectionstyle{Backend Frameworks}}{}{\strut\subsectionstyle{Databases}}
\cvdoubleitem{> 13 years}{Hibernate}{> 8 years\cbstart}{Oracle}
\cvdoubleitem{> 5 years}{Java EE}{> 5 years}{MySQL, MariaDB, H2}
\cvdoubleitem{> 3 years}{Spring Boot, Camunda}{> 3 years}{PostgreSQL, Derby}
\cvdoubleitem{> 2 years}{Quarkus}{> 1 year}{NoSQL (Neo4j, MongoDB, Redis)}
\cvdoubleitem{> 1 year}{OSGi, NodeJS}{\cbend}{}
\cvspace

\cvdoubleitem{}{\strut\subsectionstyle{Tools}}{}{\strut\subsectionstyle{Frontend Frameworks}}
\cvdoubleitem{> 13 years}{JIRA, Confluence, Maven, Jenkins}{> 5 years\cbstart}{JSF}
\cvdoubleitem{> 8 years}{Git, GitLab, Mercurial}{> 3 years}{Angular, Vaadin}
\cvdoubleitem{> 3 years}{Docker}{}{}
\cvdoubleitem{> 2 years}{Terraform}{\cbend}{}

%----------------------------------------------------------------------------------------
%	OWN PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Own Projects}

\cvitem{\textbf{Cryptonify}}{A platform-independent, fully-featured, offline password manager, including syncing, browser extensions, and an Android App.}
\cvitem{\iconLink}{\link{https://mcarle.io/project/cryptonify}}
\cvspace

\cvitem{\textbf{GetFav}}{A simple to use online service to retrieve any favicon from every public website.}
\cvitem{\iconLink}{\link{https://mcarle.io/project/getfav}}
\cvspace

\cvitem{\textbf{More on GitHub}}{
    On my GitHub account, I publish smaller projects like \emph{Strix}, a lightweight and simple JPA transaction library,
    or \emph{Sciurus}, a collection of useful aspects to, e.g., monitor method executions.
    There you will also find e.g. the source code for my website and this CV.
}
\cvitem{\iconLink}{\link{https://github.com/mcarleio}}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\cvitemize{Badminton}{Cloud \& Serverless}{Software Development}
\cvitemize{CI/CD}{Java User Groups}{Conferences}
\cvitemize{Reading}{Scuba Diving}{}

%----------------------------------------------------------------------------------------